SAT Competition 2020\tnoteref{title}

### 2021-01-03 paper/main.tex
typos

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{multirow,makecell}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{tkz-graph}
\usepackage{lscape} 
\usepackage[binary-units=true]{siunitx}

@@

Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
Despite its complexity, there is ongoing progress in solving methods and their implementations in SAT solvers. 
The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.

@@

In this competition, we initiated a new application-specific subtrack. 
The idea is to provide a large amount of benchmark instances of a specific application, and to evaluate all solvers with respect to these instance in a special track. 
In this competition, we used 200 instances of the planning domain to run a planning subtrack.

@@

This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
Moreover, while acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
is interesting, it is not the focus of the SAT competition.

@@

\label{sec:computing}
The Main Track with its sub-tracks was run on the StarExec cluster \cite{starexec},
whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
(In the Main track, validation then continued for up to \SI{45000}{\second}.)
The solvers were allowed to use up to the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition.}

@@

By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
In order to compile a balanced set of $300$ benchmark instances, we considered a maximium of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

@@

\subsection{Similarity of Solvers}
To investigate how similar the solvers of the main track are to each other, we
define a similarity metric based on the measured runtimes. For that we first
remove $186$ benchmarks from the collected data that have not been solved by any
solver. For the rest of the benchmarks we use the PAR-2 score,
% based on the \num{5000}-second timeout
i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
This leaves us with $414$ floats
$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
and $B$, normalized to the interval $[0,1]$ is defined
% as:
by Equation~\ref{eq-similarity}.

@@

In the following we provide an overview on the participating teams and solvers,  and summarize new strategies which are implemented in the award winning solvers of this competition.

>>>>

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{multirow,makecell}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}

\usepackage{lscape} 
\usepackage[binary-units=true]{siunitx}

@@

Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
Despite its complexity, there is an ongoing progress in solving methods and their implementations in SAT solvers. 
The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.

@@

In this competition, we initiated a new application-specific sub-track. 
The idea is to provide a large amount of benchmark instances of a specific application and to evaluate all solvers with respect to these instance in a special track. 
In this competition, we used 200 instances of the planning domain to run a planning sub-track.

@@

This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
Moreover, while we acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
is interesting, it is not the focus of the SAT competition.

@@

\label{sec:computing}
The Main Track with its sub-tracks was run on the StarExec cluster \cite{starexec},
whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
(In the Main track, validation then continued for up to \SI{45000}{\second}.)
The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition.}

@@

By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
In order to compile a balanced set of $300$ benchmark instances, we considered a maximium of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5--7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

@@

\subsection{Similarity of Solvers}
To investigate how similar the solvers of the Main track are to each other, we
define a similarity metric based on the measured runtimes. For that we first
remove $186$ benchmarks from the collected data that have not been solved by any
solver. For the rest of the benchmarks we use the PAR-2 score,
% based on the \num{5000}-second timeout
i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
This leaves us with $414$ floats
$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
and $B$, normalized to the interval $[0,1]$ is defined
% as:
by Equation~\ref{eq-similarity}.

@@

In the following, we provide an overview of the participating teams and solvers, 
and summarize new strategies which are implemented in the award winning solvers of this competition.
